---
title: "p8105_hw4_yy2828"
name: "Yangwei Yan"
date: "10/25/2017"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r loadpackages, message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
```

```{r}
rm(list = ls())
options(tibble.print_min = 5)
```

Read in the pups dataset. The post-natal days for each developmental landmarks are stored in variable "PD_outcome".

```{r}
pups_data = read_csv("./FAS_pups.csv") %>%
  clean_names() %>%
  gather(key = "landmark", value = "PD_outcome", pd_ears:pd_walk, na.rm = TRUE) %>%
  separate(landmark, into = c("remove", "landmark"), sep = "_") %>% 
  select(-remove)
```

The collaborator will create a plot showing the distribution of post-natal days for each developmental landmark.
```{r}
library(ggridges)
pups_data %>% 
  ggplot(aes(x=PD_outcome,y=landmark)) +
    geom_density_ridges(scale=.85)
```
The ridges plot shows the distributions of post-natal days for the four developmental landmark: ears, eyes, pivot, walk. We see from the plot that the newborns develop their eyes first, in about 4 days, and the development of eyes is the slowest, in about 13 days.
